---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# yarrawater

The yarrawater package helps users explore changes in Yarra River water quality between the 1990s and 2020s.


### Purpose of the package
The **yarrawater** package helps users explore changes in **Yarra River water quality** between the **1990s** and **2020s**.  
It provides a cleaned dataset, useful plotting functions, and an interactive **Shiny app** for comparing water quality indicators such as **pH**, **Salinity as EC@25**, **Turbidity**, and **Water Temperature**.

---

### Example of use

```{r example, eval=FALSE}
library(yarrawater)

# Launch the interactive Shiny app
run_my_app()

# Create a static summary plot
plot_yarra_data()
```
These tools help users visualise how different water parameters have changed over time.

### Installation

You can install the package directly from GitHub using the remotes package:

```{r}
# install.packages("remotes")

remotes::install_github("ETC5523-2025/assignment-4-packages-and-shiny-apps-nana0119")
library(yarrawater)

```

### Overview of the package

- Data:
yarra_wq_clean — cleaned Yarra River water quality dataset.

- Functions:

run_app() — launches the interactive Shiny dashboard.

plot_yarra_data() — creates plots comparing the 1990s and 2020s.

- Shiny:
Located in inst/shiny-app/, allowing users to select parameters and plot types interactively.

- Documentation:
All functions and data objects are clearly documented using roxygen2.

- pkgdown website:
<https://etc5523-2025.github.io/assignment-4-packages-and-shiny-apps-nana0119/>
