---
title: "Introduction to the yarrawater package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to yarrawater}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Vignettes

Vignettes show **how to use a package in practice**, not just how each function works.  
The `yarrawater` vignettes give short, example-based guides to explore water-quality data and the interactive app.

---

## About the package

`yarrawater` provides a cleaned version of Yarra River water-quality data,  
together with an interactive Shiny app for quick visual exploration.  

You can load the data directly:

```{r}
library(yarrawater)
data("yarra_wq_clean", package = "yarrawater")
```
view it:
```{r}
dplyr::glimpse(yarra_wq_clean)
```

## Basic analysis

Learn how to:

summarise and visualise water-quality indicators such as pH or turbidity,compare values between decades or sites,and interpret boxplots to understand long-term changes.




## Interactive app
You can also explore the dataset interactively with:

yarrawater::run_my_app()

The app lets you:

- select parameters

- read explanations about what the outputs mean.

## Further reading

- Data cleaning and structure — How the raw data is processed (see data-raw/yarra_wq_clean.R).

- Custom styling — Change colors and layout through www/style.css.

- Extending the package — Add your own data cleaning scripts or new datasets.

## Summary

`yarrawater` offers an end-to-end workflow:

Clean data -> Explore -> Visualize -> Interact

Try loading the data, making a simple plot, and then using the app for deeper exploration.
